
Periodic structures
========================================================


```{r, echo=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
```

```{r, echo=FALSE}
# Input 
Al_wysokosc <- read.delim("data/01_Aluminium_wysokosc", header=F, dec=",")
Al_period <- read.delim("data/01_Aluminium_period", header=F, dec=",")
PCDTBT_wysokosc <- read.delim("data/02_PCDTBT_wysokosc", header=F, dec=",")
PCDTBT_period <- read.delim("data/02_PCDTBT_period", header=F, dec=",")


laczenie_danych <- function(plik, opis_columny, opis_materialu){
    row.names(plik) <- NULL
    colnames(plik) <- opis_columny
    plik$Name <-  opis_materialu
    return(plik)
}

Al_wysokosc = laczenie_danych(Al_wysokosc, "Height", "Al")
Al_period = laczenie_danych(Al_period, "period", "Al")


PCDTBT_wysokosc = laczenie_danych(PCDTBT_wysokosc, "Height", "PCDBTB")
PCDTBT_period = laczenie_danych(PCDTBT_period, "period", "PCDTBT")

period <- NULL
period <- bind_rows(Al_period, PCDTBT_period)

wysokosc <- NULL
wysokosc <- bind_rows(Al_wysokosc,PCDTBT_wysokosc )

profil_Al_przeskalowane <- read.delim("data/profil_Al_przeskalowane.txt", header=F)

profil_PCBFDTB_przeskalowane <- read.delim("data/profil_PCBFDTB_przeskalowane.txt", header=F)
```

## Morphology analysis 
> Based on AFM images - determined the height and period of structures

### Height
```{r, echo=FALSE, message=FALSE}
# Distribution
ggplot(wysokosc, aes(Name, Height)) + 
  geom_boxplot() + geom_dotplot(binaxis = "y", stackdir = "center", position = "dodge",  dotsize = 0.5, fill="red")+
  theme_bw(base_size = 28) +
  xlab("") + 
  ylab("Height (nm)")

wysokosc %>% 
  group_by(Name) %>% 
  summarise(mean = mean(Height), sd = sd(Height))

t.test(Al_wysokosc$Height, PCDTBT_wysokosc$Height)
```

> Summary: There is the difference in height between a pure Al electrode and an active layer 

### Period
```{r, echo=FALSE, message=FALSE}
ggplot(period, aes(Name, period*1000)) +
  geom_boxplot() + geom_dotplot(binaxis = "y", stackdir = "center", position = "dodge",  dotsize = 0.5, fill="red")+
  theme_bw(base_size = 28) +
  xlab("") + 
  ylab("Period (nm)")

period %>%
group_by(Name) %>% 
  summarise(mean = mean(period), sd = sd(period))

t.test(Al_period$period,  PCDTBT_period$period)
```



```{r, echo=FALSE, message=FALSE}
rys_profil <- function(name){
        # name - profil AFM
        # os x: mikro m
        # os y: nm
  
        ggplot(name, aes(V1*10^6, V2*10^9)) +
        geom_line() + 
        theme_bw(base_size = 28) +
        ylab("z (nm)") +
        xlab(expression(paste("x (", mu, "m)"))) + 
        xlim(c(0, 5))
         }
```

### PCDTBT profile
```{r, echo=FALSE, message=FALSE}
rys_profil(profil_PCBFDTB_przeskalowane)
```

### Al profile
```{r, echo=FALSE, message=FALSE}
rys_profil(profil_Al_przeskalowane)
```




## Solar cells with periodic active layers
> Based on current-voltage charasteristics determined the devices parameters 

```{r, echo=FALSE, message=FALSE}
OPV_DVD <- read.delim("data/12_Seria_IX_RP3HT_DVD")
OPV_DVD$Solar=as.factor(OPV_DVD$Solar)
OPV_DVD = OPV_DVD[-1,]

OPV_DVD %>%
  filter(Solar == 1 | Solar == 2 )  %>%
  filter(Pixel != 4) -> OPV_flat

OPV_DVD %>% 
  filter(Solar == 3| Solar == 4) %>%
  filter(Pixel != 4) -> OPV_imprinted

OPV_flat$Ref = "Flat"
OPV_imprinted$Ref = "Imprinted"
OPV = bind_rows(OPV_flat, OPV_imprinted)
```


### Compare flat active layer to imprinted active layer (DVD structures)
```{r, echo=FALSE, message=FALSE}

ggplot(OPV, aes(Ref, Isc_1))+
  geom_boxplot() + geom_dotplot(binaxis = "y", stackdir = "center", position = "dodge",  dotsize = 0.5, fill="red")+
  theme_bw(base_size = 28) +
  xlab("") + 
  ylab(expression(paste("Isc (", mA/cm^{2}, ")", sep = " ")))



OPV %>% 
  filter(Pixel != 4)%>%
  group_by(Ref) %>%
  summarise(mean_isc = mean(Isc_1), sd_isc = sd(Isc_1), mean_Voc_1 = mean(Voc_1), sd_Voc_1 = sd(Voc_1), mean_ff = mean(FF_1), sd_ff = sd(FF_1), mean_eff = mean(EFF_1), sd_Eff = sd(EFF_1), n = length(Isc_1)) 


t.test(OPV_flat$Isc_1, OPV_imprinted$Isc_1 )
```
> Summary: There is a difference in Isc between imprinted and flat layers. The higher results were obtained for imprinted layers.  




```{r, echo=FALSE, message=FALSE}
rys_boxplot_isc <- function(name, limits){
  ggplot(name, aes(Ref, Isc_1))+
  geom_boxplot()+
  stat_summary(fun.y=mean, geom="point", shape=23, size=4) + 
  ylab(expression(paste("Jsc (", mA/cm^{2}, ")", sep = " ")))+
  xlab("")+
  scale_x_discrete(limits=limits)+
  theme_bw(base_size = 28)

  
}

rys_boxplot_voc <- function(name,limits){
  ggplot(name, aes(Ref, Voc_1))+
  geom_boxplot()+
  stat_summary(fun.y=mean, geom="point", shape=23, size=4) + 
  ylab("Voc (V)")+
  xlab("")+
  scale_x_discrete(limits=limits)+
  theme_bw(base_size = 28)

}

rys_boxplot_ff <- function(name, limits){
  ggplot(name, aes(Ref, FF_1))+
  geom_boxplot()+
  stat_summary(fun.y=mean, geom="point", shape=23, size=4) + 
  ylab("FF (%)")+
  xlab("")+
  scale_x_discrete(limits=limits)+
  theme_bw(base_size = 28)

}


rys_boxplot_eff <- function(name, limits){
  ggplot(name, aes(Ref, EFF_1))+
  geom_boxplot()+
  stat_summary(fun.y=mean, geom="point", shape=23, size=4) + 
  ylab("Efficiency(%)")+
  xlab("")+
  scale_x_discrete(limits=limits)+
      theme_bw(base_size = 28)

}

rys_boxplot <- function(name, limits){
  print(rys_boxplot_isc(name, limits))
  print(rys_boxplot_voc(name, limits))
  print(rys_boxplot_ff (name, limits))
  print(rys_boxplot_eff(name,limits))
}





```
### Summary boxplots 
```{r, echo=FALSE, message=FALSE}
limits = c("Flat","Imprinted")
rys_boxplot(OPV, limits)
```

### Characterisitcs
> Example of I-V characteristics for flat and imprinted layer

```{r, echo=FALSE, message=FALSE}
OSIX_ogn3_piks1 <- read.csv("data/S_OSIX_ogn3_piks_1_DVD.dat", sep="")
OSIX_ogn3_piks1$Ref = "Imprinted"

OSIX_ogn2_piks5 <- read.csv("data/S_OSIX_ogn2_piks_5.dat", sep="")
OSIX_ogn2_piks5$Ref= "Flat"

OSIX_charcteristic = bind_rows(OSIX_ogn3_piks1, OSIX_ogn2_piks5)

Fig_characteristics <- function(data){
  labels=c("Flat", "Imprinted")
  
  ggplot(data, aes(voltage, current_na_cm2, color = Ref))+
  geom_hline(yintercept = 0) +
  geom_line(size=1)+
  geom_point(aes(shape=Ref), size=3)+
  ylab(expression(paste("Isc (", mA/cm^{2}, ")", sep = " ")))+
  xlab("Voltage (V)")+
  coord_cartesian(ylim=c(-4.5, 10.5), xlim = c(0,0.75))+
  scale_y_continuous(breaks=seq(-4,10, 2))+
  scale_color_discrete(name="Active layer", limits=labels, labels=labels, h=c(0,240)+15)+
  scale_shape_discrete(name="Active layer", limits=labels, labels=labels)+
  guides(colour = guide_legend(override.aes = list(size=5, linetype=0)))+
  theme_bw(base_size = 20)+
  theme(legend.position = "top")

}
  

Fig_characteristics(OSIX_charcteristic)
```




